\documentclass[10pt,a4paper]{article}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage[utf8x]{inputenc}
\usepackage{ucs}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{hyperref}
\author{Robert C. Senkbeil}

% ===========================
% = RESUME INFORMATION      =
% ===========================
\newcommand{\nameemail}[2]{           % =======================================================
    \begin{center}                    % = Command:    \nameemail                              =
        {\bf \huge #1} \\             % = Purpose:    Displays the name and email provided    =
        {\bf \large #2}               % =                 as arguments.                       =
    \end{center}                      % =                                                     =
}                                     % =   Usage:    \nameemail{name}{email}                 =
                                      % =======================================================

\newcommand{\address}[2]{             % =======================================================
    \noindent                         % = Command:    \address                                =
    \begin{minipage}                  % = Purpose:    Displays the current and permanent      =
        {0.75\textwidth}              % =                 addresses in a two-column format.   =
        \begin{flushleft}             % =                                                     =
            {\bf Current Address:}    % =   Usage:    \address{Current}{Permanent}            =
            \\ #1                     % =                                                     =
        \end{flushleft}               % =                                                     =
    \end{minipage}                    % =                                                     =
    \hfill                            % =                                                     =
    \begin{minipage}                  % =                                                     =
        {0.25\textwidth}              % =                                                     =
        \begin{flushleft}             % =                                                     =    
            {\bf Permanent Address:}  % =                                                     =
            \\ #2                     % =                                                     =
        \end{flushleft}               % =                                                     =
    \end{minipage}                    % =                                                     =
}                                     % =======================================================

\newcommand{\resumesection}[2]{       % =======================================================
    \noindent                         % = Command:    \resumesection                          =
    \begin{minipage}[t]               % = Purpose:    Displays the name of the section and    =
        {0.15\textwidth}              % =                the information associated with it.  =  
        \begin{flushleft}             % =                                                     =
            {\bf #1}                  % =   Usage:    \resumesection{Section}{Information}    =
        \end{flushleft}               % =                                                     =
    \end{minipage}                    % =                                                     =
    \hfill                            % =                                                     =
    \begin{minipage}[t]               % =                                                     =
        {0.85\textwidth}              % =                                                     =
        \begin{flushleft}             % =                                                     =    
            #2                        % =                                                     =
        \end{flushleft}               % =                                                     =
    \end{minipage}                    % =                                                     =
}                                     % =======================================================

\newenvironment{resumeinfo}[3]        % =======================================================
    {\noindent {\bf #1}, #2 #3        % = Command:    \resumeinfo                             =
     \begin{itemize}                  % = Purpose:    Displays the name in a bolded style     =
         [noitemsep,nolistsep]}       % =                 with two additional pieces of       =
    {\end{itemize}}                   % =                 information to the right. Also      =
                                      % =                 allows adding a list of content     =
                                      % =                 that will be bulleted.              =
                                      % =                                                     =
                                      % =   Usage:    \begin{resumeinfo}{Bold}{Text}{Text}    =
                                      % =                 \item ...                           =
                                      % =                 \item ...                           =
                                      % =             \end{resumeinfo}                        =
                                      % =======================================================

\newcommand{\resumeline}[1]
    {\noindent #1 \\}
  
\newenvironment{collist}
    {\begin{multicols}{2}
     \begin{itemize}
         [noitemsep,nolistsep]
     \setlength{\leftmargin}{0pt}}
    {\end{itemize}
     \end{multicols}}
   
\newcommand{\tab}{\hspace*{2em}}

% ===========================
% = START OF DOCUMENT       =
% ===========================
\begin{document}
\thispagestyle{empty}

% ===========================
% = NAME & EMAIL            =
% ===========================
\nameemail{
    Robert C. Senkbeil
} {
    rcsvt@vt.edu
}

% ===========================
% = CURRENT ADDRESS &       =
% = PERMANENT ADDRESS       =
% ===========================
\address{
    208 Tech Village Drive Apt. J \\
    Blacksburg, VA 24060       \\
    (256) 283-4357
} {
    21 Christopher Way           \\
    Anniston, AL 36207           \\
    (256) 283-4357
}

% ===========================
% = EDUCATION               =
% ===========================
\resumesection
    {Education} {
     \resumeline{Virginia Polytechnic Institute and State University, Blacksburg VA}
     \resumeline{\hspace{1em} $\bullet$ Overall GPA of 3.83}
     \resumeline{{\bf B.S., Computer Engineering}, expected December 2013}
     \resumeline{\hspace{1em} $\bullet$ In-major GPA of 3.74}
     \resumeline{{\bf B.S., Computer Science}, graduated summa cum laude, May 2013}
     \resumeline{\hspace{1em} $\bullet$ In-major GPA of 4.0}
    }

% ===========================
% = WORK EXPERIENCE         =
% ===========================
\addvspace{1em}
\resumesection
    {Work Experience} {
     \begin{resumeinfo}{IBM Extreme Blue Internship}{IBM 501, RTP, NC}{Summer 2013}
         \item Worked on cloud-based monitoring, analysis of problems on an application level,
               and providing solutions to application-level problems.
         \item Wrote a RESTful API with the Ruby (1.9) language.
         \item Wrote unit tests with proper mocking of material using Ruby's MiniTest library.
         \item Worked with the Lucene query language for unstructured data.
         \item Wrote additional documentation using Markdown syntax.
         \item Constructed a Ruby Gem for the product so it could be packaged and shipped quickly.
         \item Conceptualized a unique mobile user experience to display data in an
               uncluttered and simplistic manner.
         \item Gained experience with pitch-oriented presentations for a product by presenting
               to IBM vice presidents and fellows.
     \end{resumeinfo}
     \addvspace{1em}
     \begin{resumeinfo}{CS 3114 Undergraduate TA}{Virginia Tech, Blacksburg, VA}{Spring 2013}
         \item Aided undergraduate students with course material and assignments
               involving advanced data structures and search algorithms, particularly using
               the Java language.
     \end{resumeinfo}
     \addvspace{1em}
     \begin{resumeinfo}{IBM Rational Quality Manager Co-Op}{IBM 501, RTP, NC}{Summer/Fall 2012}
         \item Worked on Rational Quality Manager defects and enhancements written in Java.
         \item Worked on RQM Import Tool for Microsoft Word/Excel defects and enhancements
               written in C\#.
         \item Gained experience with industry team communication and large-scale product development.
         \item Worked with Rational Team Concert for source control, reporting, and task management.
     \end{resumeinfo}
     \addvspace{1em}
     \begin{resumeinfo}{Microprocessor Platform Evaluation}{Virginia Tech, Blacksburg, VA}{Spring 2011}
         \item Tested features and reported the pros and cons of various microprocessor boards
               being considered as replacements for the Spartan 3E Starter Board.
         \item Wrote hardware-oriented test code in C.
     \end{resumeinfo}
    }
    
% ===========================
% = COURSE PROJECTS         =
% ===========================
\addvspace{1em}
\resumesection
    {Course Projects} {
     \begin{resumeinfo}{ECE 4534: Embedded System Design}{C}{Spring 2013}
         \item Designed and wrote code for ARM and PIC processors that interfaced with XBee
               wireless devices, Sabretooth motor controllers, and Sharp IR sensors to navigate
               a four-wheel rover through a maze and perform more efficiently on additional runs.
         \item Designed APIs for communication between various hardware devices in both wired
               and wireless conditions.
         \item Wrote I\textsuperscript{2}C communication APIs at a bit level for PIC processors.
         \item Designed and wrote a wireless communication state machine where packets of data
               were bundled with a checksum and additional verification bytes used to validate
               the contents of a packet.
         \item Wrote timer-based sensor communication for Sharp IR sensors.
         \item Wrote state-defending code to ensure that PIC processors remained in valid states
               during the rover's navigation.
         \item Video: \url{http://youtu.be/vfqsfTlCoaM}
     \end{resumeinfo}
     \addvspace{1em}
     \begin{resumeinfo}{CS 4104: Data and Algorithm Analysis}{Pseudo Code}{Spring 2013}
         \item Demonstrated an understanding of dynamic programming.
         \item Demonstrated an understanding of greedy algorithms.
         \item Demonstrated an understanding of proving problems as NP-complete.
     \end{resumeinfo}
     \addvspace{1em}
     \begin{resumeinfo}{CS 4644: Creative Computing Studio}{Unity}{Spring 2012}
         \item Designed a 3D video game to be presented at the end of the semester.
         \item Gained experience working with other majors such as art, music, and education.
     \end{resumeinfo}
     \addvspace{1em}
     \begin{resumeinfo}{CS 4204: Computer Graphics}{C++}{Spring 2012}
         \item Project 1: Use tree-based modeling to render a 3D robot with OpenGL.
         \item Project 2: Demonstrate an understanding of lighting, textures, and material
               effects with the 3D robot of project 1 using OpenGL.
         \item Project 3: Demonstrate an understanding of keyframes, tweening algorithms, and
               framerate locking by providing functionality to create animations with the robot
               from project 2.
         \item Project 4: Demonstrate an understanding of OpenGL shaders by rendering a
               texture as a wavy surface and mapping another texture onto it using vertex and
               fragment shaders.
     \end{resumeinfo}
     \addvspace{1em}
     \begin{resumeinfo}{CS 3214: Introduction to Computer Systems}{ASM \& C}{Spring 2012}
         \item Gained experience stepping through assembly and understanding how C
               translates to it and vice versa.
         \item Gained experience with shell development by creating a generic shell capable of
               managing jobs, providing builtin commands, and providing extra commands
               through custom plugins.
         \item Gained experience with memory handling by designing malloc, realloc, and free
               functions.
         \item Gained experience with threading by designing a thread pool.
         \item Gained experience with HTTP servers by writing a simple server capable of file
               serving and running some information-retrieving processes and replying to
               requests in HTTP 1.0/1.1.
     \end{resumeinfo}
     \addvspace{1em}
     \begin{resumeinfo}{CS 3114: Data Structures \& Algorithms 2}{Java}{Fall 2011}
         \item Project 1: Virtual buffer pool to simulate memory insertion, deletion, and sorting.
         \item Project 2: Quad tree written to provide spacial sorting for geographic locations.
         \item Project 3: External sorting using an external heapsort.
         \item Project 4: Sorting geographic information using external sorting of quad trees and
               BSTs using a buffer pool to maintain changes to write back to files.
     \end{resumeinfo}
    }

% ===========================
% = UNDERGRADUATE RESEARCH  =
% ===========================
\addvspace{1em}
\resumesection
    {Undergrad Research} {
     \begin{resumeinfo}{Auburn Unmanned Aerial Vehicle Research}{Auburn, AL}{Summer 2011}
         \item Researched various collision avoidance algorithms and determined possible ways they could be
               applied to real-time UAV flight.
         \item Assembled auto-pilot boards to be integrated with UAVs.
         \item Implemented a physics-inspired algorithm in C++ to work with the ROS Framework used by 
               the UAVs.
         \item Won competition between three teams for best algorithm performance.
     \end{resumeinfo}
     \addvspace{1em}
     \begin{resumeinfo}{Web-CAT Javassist Research}{Virginia Tech, Blacksburg, VA}{Fall 2010}
         \item Researched ways of using Javassist libraries to dynamically alter bytecode when loading
               class files.
         \item Used Javassist libraries to alter student-written test cases to use reflective-based
               libraries.
     \end{resumeinfo}
    }
    
% ===========================
% = SIDE PROJECTS           =
% ===========================
\addvspace{1em}
\resumesection
    {Side Projects} {
     \begin{resumeinfo}{ACM Website}{HTML 5, CSS 3, Javascript, Markdown, Eco}{Fall 2013}
         \item Wrote base ACM website for Virginia Tech during a weekend.
         \item Used semantic HTML 5 and CSS 3 (rounded borders).
         \item Wrote Javascript to integrate with Google's Calendar through a REST API
               and update the page using AJAX techniques.
         \item Statically templated the website using Docpad and languages like Markdown
               and Eco (embed Coffeescript logic in your markup).
     \end{resumeinfo}
    }  

% ===========================
% = ACTIVITIES              =
% ===========================
\addvspace{1em}
\resumesection
    {Activities} {
     \resumeline{Autonomous Mastery Prototyping Lab, 2013 \\
         \tab (Meeting Leader, 2013)}
     \resumeline{Virginia Tech Gaming Project, 2010 – 2013 \\
         \tab (President, 2011 – 2012), (Vice-President, 2010 – 2011)}
     \resumeline{Association for Computing Machinery, 2009 – 2013 \\
         \tab (President, 2013), (Webmaster, 2011 – 2013)}
     \resumeline{Institute of Electrical and Electronics Engineers, 2010 – 2013}
     \resumeline{Big Event Participant, 2012 – 2013}
     \resumeline{Hokie Camp Counselor, Summer 2010}
    }

% ===========================
% = HONORS                  =
% ===========================
\vspace{-0.5em}
\addvspace{1em}
\resumesection
    {Honors} {
     \resumeline{Phi Beta Kappa, 2013}
     \resumeline{Upsilon Pi Epsilon, 2012 – 2013}
     \resumeline{Tau Beta Pi, 2010 – 2013}
     \resumeline{Juanarena Scholarship, 2010 – 2011}
     \resumeline{Eta Kappa Nu Electrical and Computer Engineering Honor Society, 2010 – 2013 \\
         \tab (Webmaster, 2010 – 2012), (IEEE Representative, 2010 – 2011), \\
         \tab (Recruitment Officer, 2011 – 2012), (Service Chair, 2011 – 2012)}
     \resumeline{Phi Kappa Phi, 2011 – 2013}
     \resumeline{Golden Key, 2010 – 2013}
     \resumeline{National Society of Collegiate Scholars, 2010 – 2013}
     \resumeline{University Honors Program, 2009 – 2013}
     \resumeline{Dean’s List with Distinction, Spring 2010, Fall 2010, Fall 2011, Spring 2012}
     \resumeline{Dean’s List, Fall 2009, Spring 2011, Spring 2013}\vspace{-2em}
    }

% ===========================
% = END OF DOCUMENT         =
% ===========================
\end{document}
